### 2021-06-15 README.Rmd
updated the README with the code coverage badge

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?token=zA4xhwrbzL7YLqiktuAB&branch=main)](https://travis-ci.com/srmatth/mshap)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)
[![codecov](https://codecov.io/gh/srmatth/mshap/branch/main/graph/badge.svg?token=80MEJIXXX9)](https://codecov.io/gh/srmatth/mshap)
<!-- badges: end -->
